SAT Solving for Vesicle Traffic Systems in Cells

### 2017-06-18 paper/intro.tex
fix

We have implemented the encoding using Z3~\cite{z3} python API and searched for
VTS satisfying various properties upto size \ankit{....} nodes as compare
earlier tool that could only search graph upto size 6 nodes.
%
Since most VTSs in the cells are less than \ankit{....} nodes,
our tool will be useful for biologists to study VTSs.
%
Furthermore, our encoding supports several variations of
the conditions.

>>>>

We have implemented the encoding using Z3~\cite{z3} python API and searched for
VTS satisfying various properties upto size \ankit{15} nodes as compare
earlier tool that could only search graph upto size 8 nodes.
%
Since most VTSs in the cells are less than \ankit{10} nodes,
our tool will be useful for biologists to study VTSs.
%
Furthermore, our encoding supports several variations of
the conditions.

### 2017-06-18 paper/related.tex
fix

\ankit{related work: other SAT works related to bio; Graph problems; Models of VTS/GRN}
\begin{enumerate}
\item Reasoning over Biological Networks using Maximum Satisfiability.
\item BioGraphE: high-performance bionetwork analysis using the Biological Graph Environment.
\item Generalized k-ary tanglegrams on level graphs: A satisfiability-based approach and its evaluation.
\item Faster than classical quantum algorithm for dense formulas of exact
satisfiability and occupation problems.
\item Model Checking Gene Regulatory Networks.
\item SMT-Based Analysis of Biological Computation.
\item A SAT-based algorithm for finding attractors in synchronous Boolean networks.
\item ILP/SMT-Based Method for Design of Boolean Networks Based on Singleton Attractors.
\item Efficient parameter search for qualitative models of regulatory networks using symbolic model checking.
\end{enumerate}
Who will do the related work?

>>>>

\ankit{related work: other SAT works related to bio; Graph problems; Models of VTS/GRN}

\textbf{SAT, Bio and Graph}
\begin{enumerate}
\item Reasoning over Biological Networks using Maximum Satisfiability.
\item BioGraphE: high-performance bionetwork analysis using the Biological Graph Environment.
\item Generalized k-ary tanglegrams on level graphs: A satisfiability-based approach and its evaluation.
\item SMT-Based Analysis of Biological Computation.
\item A SAT-based algorithm for finding attractors in synchronous Boolean networks.
\item ILP/SMT-Based Method for Design of Boolean Networks Based on Singleton Attractors.
\item Exact DFA Identification Using SAT Solvers
\item Timing Robustness in the Budding and Fission Yeast Cell Cycles.
\end{enumerate}

\textbf{GNR and SAT}
\begin{enumerate}
\item Model Checking Gene Regulatory Networks.
\item Inference of Boolean Networks from Gene Interaction Graphs Using a SAT Solver
\item Efficient parameter search for qualitative models of regulatory networks using symbolic model checking.
\end{enumerate}

Who will do the related work?
